experDesign: helping performing experiments on batches

### 2021-04-20 paper.Rmd
Update with code

@@

In addition to distribute the samples on batches *experDesign* provides with tools to add technical replicates.
When the design is already done then the replicates are called technical replicates [@blainey2014].
Technical replicates are samples that are measured multiple times and allow to reduce the uncertainty of the measurement.
If the technical replicates are distributed on several batches they allow to measure the batch effect and thus minimize it.
To select the technical replicates needed and from which samples the function `extreme_cases` is provided.
For easier usage the `replicates` designs an experiment with the number of replicates per batch desired.

>>>>

```{r setup}
knitr::opts_chunk$set(collapse = TRUE, warning = TRUE, error = TRUE)
```

@@

In addition to distribute the samples on batches *experDesign* provides with tools to add technical replicates.
When the design is already done then the replicates are called technical replicates [@blainey2014].
Technical replicates are samples that are measured multiple times and allow to reduce the uncertainty of the measurement.
If the technical replicates are distributed on several batches they allow to measure the batch effect and thus minimize it.
To select the technical replicates needed and choose from which samples they are done the function `extreme_cases` is provided.
For easier usage the `replicates` designs an experiment with the number of replicates per batch desired.
